---
<<<<<<< HEAD
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



## What is mean total number of steps taken per day?



## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
=======
title: "Reproducible Research:Peer Assessment 1"
output: html_document
keep_md: true
---

```{r setoptions, echo = FALSE}
library(knitr)
opts_chunk$set(echo = TRUE)
```

## 1-Loading and preprocessing the data  
  
```{r load}
# Download and read data
url <- "https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip"
download.file(url,destfile = "Project1.zip")
t1 <- read.table(unz("Project1.zip","activity.csv"), header=T, sep=",")
```

```{r preproccess}
# Transform data to table dataframe and remove NA
library(dplyr)
t2 <- tbl_df(t1)
t3 <- t2[complete.cases(t2), ]
```
  
  
## 2-What is mean total number of steps per day?  
  
### Histogram of the total number of steps taken each day.
```{r hist1}
t4 <- t3%>%
    group_by(date) %>%
    summarise(stepseachday=sum(steps))
hist(t4$stepseachday,xlab = "Number of steps", main = "Steps each day")
```

### Median and mean of all steps taken per day
```{r medianandmean1}
summarise(t4, median=median(stepseachday),mean=mean(stepseachday))
```
  
  
## 3-What is the average daily activity pattern?    
  
### Time series plot of the 5-min interval and the average number of steps across all days.
```{r plot1}
t5 <- t3%>%
    group_by(interval) %>%
    summarise(av=mean(steps))
with(t5,plot(interval,av,type = "l",xlab = "5-minute interval",ylab = "average of steps"))
```
  
### 5 minute interval with the maximum number of steps on average.
```{r intervalmax}
t6 <- arrange(t5, desc(av))
t6[1,1]
```
   
  
## 4-Imputing missing values  
  
```{r missingval}
## Calculate the number of missing values in the dataset
v1 <- is.na(t1[,1])
sum(v1,na.rm = TRUE)
```
```{r fillmissingval}
## Fill in the missing values with the mean of the steps for 5-minute interval.
t7 <- merge(x=t2,y=t5,by="interval")
t8 <- t7%>%
    mutate(steps=as.double(steps)) %>%
    mutate(steps = case_when(is.na(steps)==TRUE~av,
                              TRUE~steps)) %>%
    select(steps,date,interval)
```
  
### Histogram of the total number of steps taken each day
```{r hist2}
t9 <- t8%>%
    group_by(date) %>%
    summarise(stepseachday=sum(steps))
hist(t9$stepseachday,xlab = "Number of steps", main = "Steps each day")
```
  
### Median and mean of all steps taken per day
```{r medianandmean2}
summarise(t9, median=median(stepseachday),mean=mean(stepseachday))
```
  
**These values don't differ from the values taken without missing values.**
  
  
## 5-Are there difference in activity patterns between weekdays and weekends?  
  
```{r typeday}
##Create a new factor variable with the levels "weekday" and "weekend" 
library(lubridate)
t10 <- t8%>%
    mutate(date=as.Date(date)) %>%
    mutate(typeday=wday(date))

t10<- tbl_df(t10)

tweekday <- t10 %>%
    filter(typeday %in% c(2,3,4,5,6)) %>%
    group_by(interval)%>%
    summarise(av=mean(steps)) %>%
    mutate(typeday="weekday")

tweekend <- t10%>%
    filter(typeday %in% c(1,7))%>%
    group_by(interval)%>%
    summarise(av=mean(steps))%>%
    mutate(typeday="weekend")

t11<- bind_rows(tweekday,tweekend)
t12<-mutate(t11,typeday=as.factor(typeday))
```
  
### Panel plot containing a time series plot of the 5-minute interval and the average of the number of steps taken, averaged across all weekday days or weekend days.
```{r plot2}
library(lattice)
xyplot(av~interval|typeday,data=t12,layout=c(1,2),type="l",xlab="Interval",ylab="Number of steps")
```


>>>>>>> add new files
